---
title: "digit"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  md_document:
    toc: true      
---

```{r, echo=FALSE}
pacman::p_load(digit)
rinline <- function(code) { 
    sprintf('<code class="r">``` `r %s` ```</code>', code) 
} 
desc <- suppressWarnings(readLines("DESCRIPTION"))
regex <- "(^Version:\\s+)(\\d+\\.\\d+\\.\\d+)"
loc <- grep(regex, desc)
ver <- gsub(regex, "\\2", desc[loc])
verbadge <- sprintf('<a href="https://img.shields.io/badge/Version-%s-orange.svg"><img src="https://img.shields.io/badge/Version-%s-orange.svg" alt="Version"/></a></p>', ver, ver)
````

[![Build Status](https://travis-ci.org/trinker/digit.svg?branch=master)](https://travis-ci.org/trinker/digit)
[![Coverage Status](https://coveralls.io/repos/trinker/digit/badge.svg?branch=master)](https://coveralls.io/r/trinker/digit?branch=master)
`r verbadge`

**digit** contains tools to assist in the formatting of numbers for publication.  Tools include the removal of leading zeros, standardization of number of digits, and a p-value formatter.

# Installation

To download the development version of **digit**:

Download the [zip ball](https://github.com/trinker/digit/zipball/master) or [tar ball](https://github.com/trinker/digit/tarball/master), decompress and run `R CMD INSTALL` on it, or use the **pacman** package to install the development version:

```r
if (!require("pacman")) install.packages("pacman")
pacman::p_load_gh("trinker/digit")
```

# Contact

You are welcome to:
* submit suggestions and bug-reports at: <https://github.com/trinker/digit/issues>
* send a pull request on: <https://github.com/trinker/digit/>
* compose a friendly e-mail to: <tyler.rinker@gmail.com>


# Demonstration

```{r, warn=FALSE}
f(c(0.0, 0, .2, -00.02, 1.122222, pi, "A"))
```


We can see its use in actual model reproting as well:


```{r}
mod1 <- t.test(1:10, y = c(7:20))
sprintf(
    "t = %s (%s)",
    f(mod1$statistic),
    p(mod1$p.value)
)


mod2 <- t.test(1:10, y = c(7:20, 200))

sprintf(
    "t = %s (%s)",
    f(mod2$statistic, 2),
    p(mod2$p.value, digits = 2)
)
```

We can build a function to reprot model statistics:

```{r}
report <- function(mod, stat = NULL, digits = c(0, 2, 2)) {
    
    stat <- if (is.null(stat)) stat <- names(mod[["statistic"]])
    sprintf(
        "%s(%s) = %s, %s", 
        stat,
        paste(f(mod[["parameter"]], digits[1]), collapse = ", "),
        f(mod[["statistic"]], digits[2]),
        p(mod[["p.value"]], digits = digits[3])
    )

}

report(mod1)
report(oneway.test(count ~ spray, InsectSprays))
report(chisq.test(matrix(c(12, 5, 7, 7), ncol = 2)))
```

This enables in-text usage as well.  First set up the models in a code chunk:

```{r}
mymod <- oneway.test(count ~ spray, InsectSprays)
```

And then use `r rinline("report(mymod)")` resuting in a report that looks like this: `r report(mymod)`
